Fast, Scalable Phrase-Based SMT Decoding

### 2016-02-07 acl.2016/acl2016.tex
acl paper

We take a different approach by integrating the lexicalized model file into the translation model, reducing the need to query another model file. This resulted in a large decrease in decoding time, Figure~\ref{fig:lex-ro}.

>>>>

We take a different approach by integrating the lexicalized model file into the translation model, reducing the need to query another model file. This resulted in a large decrease in decoding time, especially with high number of cores, Figure~\ref{fig:lex-ro}. Integrating the lexicalized reordering model into the translation model decreases decoding time by 29\% with a single core but it is over 5 times faster using all cores. In fact, it enables the decoder to continue to scale, making efficient use of all hyperthreads, while using a separate lexicalized reordering model performance flatten out and actually worsens atfer approximately 10 threads.
